Distributed Version Control Systems

### 2010-05-16 paper.tex

Then both repositories can be merged togheter into an integration one by pulling from each of them. If there are conflicts which cannot be resolved easily, it is possible to ask the team who caused the conflict to solve it since all history is preserved. Then this team con clone the integration repository and merge it with its working repository. They can ask the person in charge to pull the changes back again.

>>>>

Then both repositories can be merged togheter into an integration one by pulling from each of them. If there are conflicts which cannot be resolved easily, it is possible to ask the team who caused the conflict to solve it since all history is preserved. Then this team can clone the integration repository and merge it with its working repository. They can ask the person in charge to pull the changes back again.

\subsection{Centralized repository with integration manager}
It is possible to have a single central repository where all developers have read access. Everyone has an official public version from which they can work from. Then, to add new change sets to the official version, an integration manager can pull the changes from each developer (or each team) to have all the changes tested and reviewed. When the build is good enough the integration manager can push the changes to the central repository so all developers have the new version available.
It is also possible to have an automatic integration manager. This server will accept pushes, run all tests and if everything is ok it will then push this changes to the central repository. Otherwise it can discard the changes and signal the developer the reasons (most likely through an email).
